---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# mastermapr

<!-- badges: start -->
<!-- badges: end -->

The goal of mastermapr is to make it easier to import data from Ordnance Survey's MasterMap products into R.

## Installation

<!-- You can install the released version of mastermapr from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("mastermapr") -->
<!-- ``` -->

Install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("itsleeds/mastermapr")
```
## Reading-in mastermap data

MasterMap products come in various formats including `.gz` (GML) and `.gpkg` (GeoPackage).
Once unzipped you can read-in MasterMap files as follows (you need to apply for a license for many of their products):

```{r example}
library(mastermapr)
## basic example code
# mm_highway = read_mastermap("~/hd/data/os/Download_mastermap-roads-2019_1483661/MasterMap Highways Network_rami_3480319/", n = 3)
# plot(mm_highway["roadClassification"])
```

### Reading Pavements

You can read pavement (sidewalk) geometries from the Topography layer using `read_pavement()`:

```r
gpkg_path = "path/to/OSMasterMapTopography_topographic_area.gpkg"
pavements = read_pavement(gpkg_path)
```

For large files, you can filter by area using a WKT string:

```r
bbox_wkt = "POLYGON((400000 400000, 401000 400000, 401000 401000, 400000 401000, 400000 400000))"
pavements = read_pavement(gpkg_path, wkt_filter = bbox_wkt)
```

## Next steps

So far this package has limited functionality but it may be expanded in the future.
Watch this space and feel free to get involved via the issue tracker if interested!
